---
title: "SEDAR 84 Trip Interview Program (TIP) Size Composition Analysis of Yellowtail Snapper (Ocyurus chrysurus) in Puerto Rico, U.S. Caribbean, 1983-2022"
format: docx
editor: visual
output-file: sedar_84_pr_yt_2022.docx
execute:
  cache: true
---

#### Katherine Godwin^1^, Adyan Rios^2^, Kyle Dettloff^3^

#### January 9, 2024

###### ^1^*Cooperative Institute for Marine & Atmospheric Studies, Rosenstiel School of Marine, Atmospheric, and Earth Science, University of Miami, 4600 Rickenbacker Causeway, Miami, FL 33149*

###### ^2^*National Marine Fisheries Service, Southeast Fisheries Science Center Sustainable Fisheries Division, 75 Virginia Beach Drive, Miami, FL 33149*

###### ^3^*National Marine Fisheries Service, Southeast Fisheries Science Center Fisheries Statistics Division, 75 Virginia Beach Drive, Miami, FL 33149*

\newpage

## Summary

```{r}
#| echo: false
#| warning: false
#| message: false

librarian::shelf(here, knitr)
# library(here)
load(here::here('tools','sedar_84_pr_yt_2022','pr_yt_2022_figures.RData'))

```

In preparation for SouthEast Data, Assessment, and Review (SEDAR) 84 Benchmark assessment of Caribbean Yellowtail Snapper in Puerto Rico, Southeast Fisheries Science Center, Sustainable Fisheries Division (SEFSC), Caribbean Fisheries Branch conducted a size composition analysis of the Trip Interview Program (TIP) data. This document summarizes data collected from 1983 to 2022.

The TIP data pertaining to Yellowtail Snapper in Puerto Rico is comprised of `r n_all_len` length observations across `r total_trip_id_unique` unique port sampling interviews. There are `r n_fork_len` fork length observations (`r p_fork_len`%). There are two parts to this document. First, gear groupings were established based on a generalized linear model (GLM) analysis using a gamma-distributed dependent variable and a covariate to account for changes in mean size over time. Second, the size composition of each gear grouping was determined. The GLM analysis of the full time series reported a statistical difference between the "LINES HAND", "HAUL SEINES", and "POTS AND TRAPS; FISH".

\newpage

## Generalized Linear Model (GLM) Analysis

The GLM analysis was first conducted on the time series as a whole (1983-2022) (@fig-abc1), and then on a truncated time series that best reflects the available species-specific commercial landings data (2012-2022) (@fig-abc2). The analyses of the full and truncated time series display the statistical similarity of all available gears with respect to the mean size of fish caught throughout the time series.

The GLM analysis of the full time series reported a statistical difference between the "LINES HAND", "HAUL SEINES", and "POTS AND TRAPS; FISH" gears (@tbl-tbl1). However, the truncated time series investigation showed statistical significance between "LINES HAND" and "POTS AND TRAPS;FISH" (@tbl-tbl2). Thus, all available gears were grouped into "HAND LINE", "HAUL SEINES", "TRAPS", or "OTHER" according to their relative similarity in usage to those of "LINES HAND", "HAUL SEINES", and "POTS AND TRAPS; FISH". It should be noted that `r p_not_coded`% of the lengths recorded over the full time series have a gear name specification of "NOT CODED". 


```{r all lengths GLM}
#| echo: false
#| label: fig-abc1
#| fig-cap: |
#|   Plot showing relative number of Yellowtail Snapper lengths in Puerto Rico across time collected. Each point is color specific to the gear it represents.
#| fig-width: 11
#| fig-height: 6 

abc1

```

\newpage

```{r all lengths GLM tbl}
#| echo: false
#| warning: false
#| label: tbl-tbl1
#| tbl-cap: |
#|   GLM analysis summary results for Puerto Rico TIP Yellowtail Snapper fork lengths(cm) from 1983 to 2022. The column titled “group” indicates the group(s) where mean lengths are not statistically different from other gears with matching group number(s). The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column indicates the percent of the total recorded lengths for each gear. 
library(knitr)
kable("")

```

```{r}
#| echo: false
#| tbl-colwidths: false
#| warning: false
library(flextable)
tbl1

```

\newpage

```{r all lengths GLM 2012}
#| echo: false
#| warning: false
#| label: fig-abc2
#| fig-cap: |
#|   Plot showing relative number of Yellowtail Snapper lengths in Puerto Rico from 2012 to 2022. Each point is color specific to the gear it represents.
#| fig-width: 12
#| fig-height: 7

abc2

```

```{r all lengths GLM tbl 2012}
#| echo: false
#| warning: false
#| label: tbl-tbl2
#| tbl-cap: |
#|   GLM analysis summary results for the TIP data of Yellowtail Snapper lengths in Puerto Rico from 2012 to 2022. The column titled “group” indicates the group(s) where mean lengths are not statistically different from other gears with matching group number(s). The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column indicates the percent of the total recorded lengths for each gear. 
library(knitr)
kable("")

```

```{r}
#| echo: false
#| tbl-colwidths: false
#| warning: false
library(flextable)
tbl2

```

\newpage

## Aggregated Gear Density

The aggregated densities of Yellowtail Snapper lengths(cm) in Puerto Rico are plotted across the full time period and by gear groupings for which GLM analyses were conducted, respectively (@fig-abc14, and @fig-abc15). Each plot includes a vertical line associated with the respective mean length. N equals the number of individuals displayed by category.

```{r all lengths agd}
#| echo: false
#| label: fig-abc14
#| fig-cap: |
#|   Aggregated density plot of lengths(cm) of Yellowtail Snapper in Puerto Rico from 1983 to 2022. Dotted line represents mean length. 
#| fig-width: 12
#| fig-height: 8

abc14

```

<!-- \newpage -->

<!-- ```{r all lengths agd} -->

<!-- #| echo: false -->

<!-- #| label: fig-abc16 -->

<!-- #| fig-cap: | -->

<!-- #|   Aggregated density plot of lengths measured in centimeters of Yellowtail Snapper in Puerto Rico from 2012 to 2022. Dotted line represents mean length.  -->

<!-- #| fig-width: 12 -->

<!-- #| fig-height: 8 -->

<!-- abc16 -->

<!-- ``` -->

\newpage

```{r diving agd}
#| echo: false
#| label: fig-abc15
#| fig-cap: |
#|   Aggregated density plot of lengths(cm) of the gear groupings for Yellowtail Snapper in Puerto Rico from 1983 to 2022. Dotted line represents mean length.
#| fig-width: 12
#| fig-height: 8

abc15

```
