---
title: "SEDAR 84 Trip Interview Program (TIP) Size Composition Analysis of Stoplight Parrotfish (Sparisoma viride) in St. Croix, U.S. Caribbean, 1983-2022"
format: docx
editor: visual
output-file: sedar_84_stx_stp_2022.docx
bibliography: references.bib
nocite: '@*'
execute:
  cache: true
---

#### Katherine Godwin^1^, Adyan Rios^2^, Kyle Dettloff^3^

#### January 9, 2024

###### ^1^*Cooperative Institute for Marine & Atmospheric Studies, Rosenstiel School of Marine, Atmospheric, and Earth Science, University of Miami, 4600 Rickenbacker Causeway, Miami, FL 33149*

###### ^2^*National Marine Fisheries Service, Southeast Fisheries Science Center Sustainable Fisheries Division, 75 Virginia Beach Drive, Miami, FL 33149*

###### ^3^*National Marine Fisheries Service, Southeast Fisheries Science Center Fisheries Statistics Division, 75 Virginia Beach Drive, Miami, FL 33149*

\newpage

## Summary

```{r}
#| echo: false
#| warning: false
#| message: false

librarian::shelf(here, knitr)
# library(here)
load(here::here('tools','sedar_84_stx_stp_2022','stx_stp_2022_figures.RData'))

```

In preparation for SouthEast Data, Assessment, and Review (SEDAR) 84 Benchmark assessment of Caribbean Stoplight Parrotfish in St. Croix, U.S. Virgin Islands; the Southeast Fisheries Science Center, Sustainable Fisheries Division (SEFSC), Caribbean Fisheries Branch conducted a size composition analysis of the Trip Interview Program (TIP) data. This document summarizes data collected from 1983 to 2022.

The TIP data pertaining to Stoplight Parrotfish in St. Croix is comprised of `r n_all_len` length observations across `r total_trip_id_unique` unique port sampling interviews, of which `r n_fork_len` are fork lengths (`r p_fork_len`%). Two analyses are described in this document. First, gear groupings were established among gears based upon Stoplight Parrotfish size composition differences among gears. Gear groups were identified based on a generalized linear model (GLM) analysis using a gamma-distributed dependent variable and a covariate to account for changes in mean size over time. Second, the aggregate density of the lengths was determined based on time series and gear representation within the data.The GLM analysis of the full time series reported a statistical difference in the size of measured fish between the "SPEARS" and "POTS AND TRAPS;FISH" gears.

\newpage

## Data Description

The Trip Interview Program (TIP) collects length and weight data from fish landed by commercial fishing vessels. Data collection began in 1983 with frequent updates in best practices; the latest being in 2017. Data are collected by trained shore-based samplers. The trained samplers interview fishermen to obtain morphometric data and biological samples from their catch. The TIP has five primary data tables: Interview, Effort, Landing, Sample, and Observation [@beggerly2022] . The Interview, Landing, and Sample tables were utilized in this document to analyze the year, region, species, interview ID, gear name, and length values. The data were filtered to Stoplight Parrotfish fork lengths in St. Croix recorded from 1983 to 2022.

## Generalized Linear Model (GLM) Analysis

The GLM analysis of landed Stoplight Parrotfish size composition among commercial fishing gears was first conducted on the time series as a whole from 1983-2022, and then on a truncated time series that best reflects the available species-specific commercial landings data from 2012-2022 (@fig-abc1). The analyses of the full and truncated time series display the statistical similarity of gears with respect to the mean size of fish caught throughout the time series. Gears with fewer than three interviews were excluded from the analysis.

The GLM analysis of the full time series reported a statistical difference between the "SPEAR" and "POTS AND TRAPS;FISH" gears (@tbl-tbl1). However, the truncated time series investigation showed no statistical significance between any of the available gears (@tbl-tbl2).

\newpage

```{r all lengths GLM}
#| echo: false
#| label: fig-abc1
#| fig-cap: |
#|   Plot showing relative number of Stoplight Parrotfish lengths collected in St. Croix over time. Each point is color specific to the gear it represents. Gears are arranged from most to least abundant. Grey vertical line denotes the beginning of the truncated time series at 2012. 
#| fig-width: 12
#| fig-height: 8

abc1

```

\newpage

```{r all lengths GLM tbl}
#| echo: false
#| warning: false
#| label: tbl-tbl1
#| tbl-cap: |
#|   GLM analysis summary results for St. Croix TIP Stoplight Parrotfish fork lengths(cm) from 1983 to 2022. The column titled “group” indicates the group(s) where mean lengths are not statistically different from other gears with matching group number(s). The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column indicates the percent of the total recorded lengths for each gear. Gears that make up less than 2% are shaded in gray.
library(knitr)
kable("")

```

```{r}
#| echo: false
#| tbl-colwidths: false
#| warning: false
library(flextable)
tbl1

```

\newpage

<!-- ```{r all lengths GLM 2012} -->

<!-- #| echo: false -->

<!-- #| label: fig-abc2 -->

<!-- #| fig-cap: | -->

<!-- #|   Plot showing relative number of Stoplight Parrotfish lengths collected in St. Croix from 2012 to 2022. Each point is color specific to the gear it represents. -->

<!-- #| fig-width: 12 -->

<!-- #| fig-height: 7 -->

<!-- abc2 -->

<!-- ``` -->

```{r all lengths GLM tbl 2012}
#| echo: false
#| warning: false
#| label: tbl-tbl2
#| tbl-cap: |
#|   GLM analysis summary results for the TIP data of Stoplight Parrotfish fork lengths in St. Croix from 2012 to 2022. The column titled “group” indicates the group(s) where mean lengths are not statistically different from other gears with matching group number(s). The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column indicates the percent of the total recorded lengths for each gear. Gears that make up less than 2% are shaded in gray.
library(knitr)
kable("")

```

```{r}
#| echo: false
#| tbl-colwidths: false
#| warning: false
library(flextable)
tbl2

```

\newpage

## Aggregated Gear Density

The aggregated densities of Stoplight Parrotfish lengths(cm) in St. Croix are plotted across the full time period and by gear groupings for which GLM analyses were conducted, respectively (@fig-abc14, and @fig-abc15). Each plot includes a vertical line associated with the respective mean length. N equals the number of individuals displayed by gear category. Gears with fewer than three interviews were excluded from the analysis. <!-- Years with fewer than 30 lengths were excluded from the annual density plot.  -->

```{r all lengths agd}
#| echo: false
#| label: fig-abc14
#| fig-cap: |
#|   Aggregated density plot of lengths(cm) of Stoplight Parrotfish in St. Croix, all gears combined. Dotted line represents mean length. 
#| fig-width: 12
#| fig-height: 8

abc14

```

<!-- \newpage -->

<!-- ```{r all lengths agd} -->

<!-- #| echo: false -->

<!-- #| label: fig-abc16 -->

<!-- #| fig-cap: | -->

<!-- #|   Aggregated density plot of lengths measured in centimeters of Stoplight Parrotfish in St. Croix from 2012 to 2022. Dotted line represents mean length.  -->

<!-- #| fig-width: 12 -->

<!-- #| fig-height: 8 -->

<!-- abc16 -->

<!-- ``` -->

\newpage

```{r diving agd}
#| echo: false
#| label: fig-abc15
#| fig-cap: |
#|   Aggregated density plot of lengths(cm)  of gears with greater than 2% representation for Stoplight Parrotfish in St. Croix from 1983 to 2022. Dotted line represents mean length.
#| fig-width: 12
#| fig-height: 8

abc15

```

```{r diving agd 2012}
#| echo: false
#| label: fig-abc19
#| fig-cap: |
#|   Aggregated density plot of lengths(cm)  of gears with greater than 2% representation for Stoplight Parrotfish in St. Croix from 2012 to 2022. Dotted line represents mean length.
#| fig-width: 12
#| fig-height: 8

abc19

```

<!-- \newpage -->

<!-- ```{r all lengths agd by yr} -->

<!-- #| echo: false -->

<!-- #| label: fig-abc17 -->

<!-- #| fig-cap: | -->

<!-- #|   Aggregated density plot of lengths(cm) of Stoplight Parrotfish in St. Croix by year, all gears combined.  -->

<!-- #| fig-width: 12 -->

<!-- #| fig-height: 12 -->

<!-- abc17 -->

<!-- ``` -->

<!-- \newpage -->

<!-- ```{r diving agd by yr} -->

<!-- #| echo: false -->

<!-- #| label: fig-abc18 -->

<!-- #| fig-cap: | -->

<!-- #|   Aggregated density plot of lengths(cm)  of gears with greater than 2% representation for Stoplight Parrotfish in St. Croix by year.  -->

<!-- #| fig-width: 12 -->

<!-- #| fig-height: 12 -->

<!-- abc18 -->

<!-- ``` -->

\newpage

## Literature Cited
