---
title: "TIP Length Comps STX STP"
format: docx
editor: visual
output-file: test.docx
execute:
  cache: true
---
# Summary 

```{r}
#| echo: false
#| warning: false
#| message: false

library(here)
source(here::here( "tools", "sedar_84_stx_stp_2022", 'stx_stp_2022_figures.R'))
source("~/SEFSC-SFD-CFB-TIP-Compositions/tools/sedar_84_stx_stp_2022/stx_stp_2022_figures.R")

```


In early (what month?) 2023, the Caribbean Fishery Management Council (CFMC) requested the assistance of the National Marine Fisheries Service (NOAA Fisheries), Southeast Fisheries Science Center (SEFSC) to conduct stoplight parrotfish assessment updates outside the SouthEast Data, Assessment, and Review (SEDAR) process. The request was to provide size composition analysis of the Trip Interview Program (TIP) data available for the St. Croix region utilizing methods established previously in SEDAR 80 (is this the origination??). This document provides size composition analysis for stoplight parrotfish in St. Croix using TIP data for the years 1988 to 2022. This work was conducted by the Southeast Fisheries Science Center, Sustainable Fisheries Division, Caribbean Fisheries Branch. 

There are two main portions of this document. First,  gear groupings were established based on a general linear model (glm) analysis. Second, the size composition of each gear grouping was assessed. 

\newpage

This report provides a summary of the procedures used to complete the size composition analysis of stoplight parrotfish in St. Croix using TIP data from 1988 to 2022. The glm analysis used a gamma-distributed dependent variable. 

\



```{r}
#| echo: false
#| label: fig-abc2
#| fig-cap: |
#|   Aggregated density plot of lengths measured in millimeters of Stoplight Parrotfish in St. Croix grouped by assigned gear groupings. 
#| fig-width: 6
#| fig-height: 3

abc2


```

\newpage

```{r}
#| echo: false
#| warning: false
#| label: tbl-abc2
#| tbl-cap: |
#|   Caribbean Spiny Lobster variable-catch (annual) and constant-catch (average) OFLs and ABCs for Puerto Rico, based on the Tier 3 of the ABC Control Rule. The column titled "Source" indicates if the rows are associated with the SEDAR 57 benchmark with input landings through 2020 or with the SEDAR 57 update with input landings through 2023. All OFLs and ABCs are in pounds whole weight.

library(knitr)
kable("")

```