---
title: "SEDAR 84 Trip Interview Program (TIP) Size Composition Analysis of Stoplight Parrotfish (Sparisoma viride) in St. Croix, U.S. Caribbean, 1983-2022"
format: docx
editor: visual
output-file: sedar_84_stx_stp_2022.docx
execute:
  cache: true
---

#### Katherine Godwin^1^, Adyan Rios^2^, Kyle Dettloff^3^

#### January 9, 2024

###### ^1^*Cooperative Institute for Marine & Atmospheric Studies, Rosenstiel School of Marine, Atmospheric, and Earth Science, University of Miami, 4600 Rickenbacker Causeway, Miami, FL 33149*

###### ^2^*National Marine Fisheries Service, Southeast Fisheries Science Center Sustainable Fisheries Division, 75 Virginia Beach Drive, Miami, FL 33149*

###### ^3^*National Marine Fisheries Service, Southeast Fisheries Science Center Fisheries Statistics Division, 75 Virginia Beach Drive, Miami, FL 33149*

\newpage

## Summary

```{r}
#| echo: false
#| warning: false
#| message: false

librarian::shelf(here, knitr)
# library(here)
load(here::here('tools','sedar_84_stx_stp_2022','stx_stp_2022_figures.RData'))

```

In preparation for SouthEast Data, Assessment, and Review (SEDAR) 84 Benchmark assessment of Caribbean Stoplight Parrotfish in St. Croix, Southeast Fisheries Science Center, Sustainable Fisheries Division (SEFSC), Caribbean Fisheries Branch conducted a size composition analysis of the Trip Interview Program (TIP) data. This document summarizes data collected from 1983 to 2022.

The TIP data pertaining to Stoplight Parrotfish in St. Croix is comprised of `r n_all_len` length observations across `r total_trip_id_unique` unique port sampling interviews, of which `r n_fork_len` are fork lengths (`r p_fork_len`%). There are two parts to this document. First, gear groupings were established based on a generalized linear model (GLM) analysis using a gamma-distributed dependent variable and a covariate to account for changes in mean size over time. Second, the size composition of each gear grouping was determined.The GLM analysis of the full time series reported a statistical difference between the "SPEARS" and "POTS AND TRAPS;FISH" gears.

\newpage

## Generalized Linear Model (GLM) Analysis

The GLM analysis was first conducted on the time series as a whole (1983-2022) (@fig-abc1), and then on a truncated time series that best reflects the available species-specific commercial landings data (2012-2022) (@fig-abc2). The analyses of the full and truncated time series display the statistical similarity of all available gears with respect to the mean size of fish caught throughout the time series.

The GLM analysis of the full time series reported a statistical difference between the "SPEAR" and "POTS AND TRAPS;FISH" gears (@tbl-tbl1). However, the truncated time series investigation showed no statistical significance between any of the available gears (@tbl-tbl2). Thus, all available gears were grouped into "DIVING" or "OTHER" according to their relative similarity in usage to those of "SPEARS" and "POTS AND TRAPS;FISH".

```{r all lengths GLM}
#| echo: false
#| label: fig-abc1
#| fig-cap: |
#|   Plot showing relative number of Stoplight Parrotfish lengths collected in St. Croix over time. Each point is color specific to the gear it represents.
#| fig-width: 12
#| fig-height: 8

abc1

```

\newpage

```{r all lengths GLM tbl}
#| echo: false
#| warning: false
#| label: tbl-tbl1
#| tbl-cap: |
#|   GLM analysis summary results for St. Croix TIP Stoplight Parrotfish fork lengths(cm) from 1983 to 2022. The column titled “group” indicates the group(s) where mean lengths are not statistically different from other gears with matching group number(s). The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column indicates the percent of the total recorded lengths for each gear. 
library(knitr)
kable("")

```

```{r}
#| echo: false
#| tbl-colwidths: false
#| warning: false
library(flextable)
tbl1

```

\newpage

```{r all lengths GLM 2012}
#| echo: false
#| label: fig-abc2
#| fig-cap: |
#|   Plot showing relative number of Stoplight Parrotfish lengths collected in St. Croix from 2012 to 2022. Each point is color specific to the gear it represents.
#| fig-width: 12
#| fig-height: 7

abc2

```

```{r all lengths GLM tbl 2012}
#| echo: false
#| warning: false
#| label: tbl-tbl2
#| tbl-cap: |
#|   GLM analysis summary results for the TIP data of Stoplight Parrotfish fork lengths in St. Croix from 2012 to 2022. The column titled “group” indicates the group(s) where mean lengths are not statistically different from other gears with matching group number(s). The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column indicates the percent of the total recorded lengths for each gear. 
library(knitr)
kable("")

```

```{r}
#| echo: false
#| tbl-colwidths: false
#| warning: false
library(flextable)
tbl2

```

\newpage

## Aggregated Gear Density

The aggregated densities of Stoplight Parrotfish lengths(cm) in St. Croix are plotted across the full time period and by gear groupings for which GLM analyses were conducted, respectively (@fig-abc14, and @fig-abc15). Each plot includes a vertical line associated with the respective mean length. N equals the number of individuals displayed by gear category.

```{r all lengths agd}
#| echo: false
#| label: fig-abc14
#| fig-cap: |
#|   Aggregated density plot of lengths(cm) of Stoplight Parrotfish in St. Croix from 1983 to 2022. Dotted line represents mean length. 
#| fig-width: 12
#| fig-height: 8

abc14

```

<!-- \newpage -->

<!-- ```{r all lengths agd} -->

<!-- #| echo: false -->

<!-- #| label: fig-abc16 -->

<!-- #| fig-cap: | -->

<!-- #|   Aggregated density plot of lengths measured in centimeters of Stoplight Parrotfish in St. Croix from 2012 to 2022. Dotted line represents mean length.  -->

<!-- #| fig-width: 12 -->

<!-- #| fig-height: 8 -->

<!-- abc16 -->

<!-- ``` -->

\newpage

```{r diving agd}
#| echo: false
#| label: fig-abc15
#| fig-cap: |
#|   Aggregated density plot of lengths(cm) of the gear groupings for Stoplight Parrotfish in St. Croix from 1983 to 2022. Dotted line represents mean length.
#| fig-width: 12
#| fig-height: 8

abc15

```
