---
title: "SEDAR 84 Trip Interview Program (TIP) Size Composition Analysis of Stoplight Parrotfish (Sparisoma viride) in St. Croix, US Caribbean, 1983-2022"
format: docx
editor: visual
output-file: test.docx
execute:
  cache: true
---

#### Katherine Godwin^1^, Adyan Rios^2^, Kyle Dettloff^3^ {style="text-align: center;"}

#### January 9, 2024 {style="text-align: center;"}

###### ^1^*Cooperative Institute for Marine & Atmospheric Studies, Rosenstiel School of Marine, Atmospheric, and Earth Science, University of Miami, 4600 Rickenbacker Causeway, Miami, FL 33149*

###### ^2^*National Marine Fisheries Service, Southeast Fisheries Science Center Sustainable Fisheries Division, 75 Virginia Beach Drive, Miami, FL 33149*

###### ^3^*what office does kyle work out of??*

\newpage

## Summary

```{r}
#| echo: false
#| warning: false
#| message: false

library(here)
source(here::here('tools','sedar_84_stx_stp_2022','stx_stp_2022_figures.R'))


```

In early (what month?) 2023, the Caribbean Fishery Management Council (CFMC) requested the assistance of the National Marine Fisheries Service (NOAA Fisheries), Southeast Fisheries Science Center (SEFSC) to conduct Stoplight Parrotfish assessment updates outside the SouthEast Data, Assessment, and Review (SEDAR) process. The request was to provide size composition analysis of the Trip Interview Program (TIP) data available for the St. Croix region utilizing methods established previously in SEDAR 80 (is this the origination??). This document provides size composition analysis for Stoplight Parrotfish in St. Croix using TIP data for the years 1988 to 2022. This work was conducted by the Southeast Fisheries Science Center, Sustainable Fisheries Division, Caribbean Fisheries Branch.

There are two main portions of this document. First, gear groupings were established based on a general linear model (glm) analysis. Second, the size composition of each gear grouping was assessed.

\newpage

This report provides a summary of the procedures used to complete the size composition analysis of Stoplight Parrotfish in St. Croix using TIP data from 1988 to 2022. The glm analysis used a gamma-distributed dependent variable.

## Generalized Linear Model (GLM) Analysis

```{r all lengths glm}
#| echo: false
#| label: fig-abc1
#| fig-cap: |
#|   Plot of all lengths measured in centimeters of Stoplight Parrotfish in St. Croix across time collected. Trend line is mapped across data, each point is color and shape specific to the gear it represents. 
#| fig-width: 12
#| fig-height: 6

abc1

```

\newpage

```{r all lengths glm tbl}
#| echo: false
#| warning: false
#| label: tbl-tbl1
#| tbl-cap: |
#|   This shows the results of glm analysis on the full TIP data set of Stoplight Parrotfish lengths in St. Croix. The column titled "group" indicates the group(s) that the gear can statistically be included in, and thus be statistically similar to the other gears grouped similarly. The "n" column indicates the number of unique lengths recorded for each gear. The "ID" column indicates the number of distinct trip ID's associated with each gear. The "Percentage" column inticates the percent(n_fish) of the total recorded fish lengths that are included within each gear. 
library(knitr)
kable("")
tbl1


```

\newpage

```{r all lengths glm 2012}
#| echo: false
#| label: fig-abc2
#| fig-cap: |
#|   Plot of all lengths measured in centimeters of Stoplight Parrotfish in St. Croix from 2012 to 2022. Trend line is mapped across data, each point is color and shape specific to the gear it represents. 
#| fig-width: 12
#| fig-height: 8

abc2

```

```{r all lengths glm tbl 2012}
#| echo: false
#| warning: false
#| label: tbl-tbl2
#| tbl-cap: |
#|   This shows the results of glm analysis on the TIP data set of Stoplight Parrotfish lengths in St. Croix from 2012 to 2022. The column titled "group" indicates the group(s) that the gear can statistically be included in, and thus be statistically similar to the other gears grouped similarly. The "n" column indicates the number of unique lengths recorded for each gear. The "ID" column indicates the number of distinct trip ID's associated with each gear. The "Percentage" column inticates the percent(n_fish) of the total recorded fish lengths that are included within each gear. 

tbl2

```

\newpage

```{r diving glm}
#| echo: false
#| label: fig-abc3
#| fig-cap: |
#|   Plot of "diving" gear group lengths measured in centimeters of Stoplight Parrotfish in St. Croix across time collected. Trend line is mapped across data, each point is color and shape specific to the gear it represents. No significant p values for time period or gears, further comparisons not needed.
#| fig-width: 12
#| fig-height: 12

abc3

```

```{r diving glm tbl}
#| echo: false
#| warning: false
#| label: tbl-tbl3
#| tbl-cap: |
#|   This shows the results of glm analysis of the "diving" gear group of Stoplight Parrotfish lengths in St. Croix. The column titled "group" indicates the group(s) that the gear can statistically be included in, and thus be statistically similar to the other gears grouped similarly. The "n" column indicates the number of unique lengths recorded for each gear. The "ID" column indicates the number of distinct trip ID's associated with each gear. The "Percentage" column inticates the percent(n_fish) of the total recorded fish lengths that are included within each gear. 

tbl3

```

\newpage

```{r trap glm}
#| echo: false
#| label: fig-abc4
#| fig-cap: |
#|   Plot of "trap" gear group lengths measured in centimeters of Stoplight Parrotfish in St. Croix across time collected. Trend line is mapped across data, each point is color and shape specific to the gear it represents. 
#| fig-width: 12
#| fig-height: 12

abc4

```

```{r trap glm tbl}
#| echo: false
#| warning: false
#| label: tbl-tbl4
#| tbl-cap: |
#|   This shows the results of glm analysis of the "trap" gear group of Stoplight Parrotfish lengths in St. Croix. The column titled "group" indicates the group(s) that the gear can statistically be included in, and thus be statistically similar to the other gears grouped similarly. The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column inticates the percent of the total(n) recorded fish lengths that are included within each gear. 

tbl4

```

\*add summary of differences between trap gears \newpage

```{r net glm}
#| echo: false
#| label: fig-abc5_fig-abc6
#| fig-cap: |
#|   Plot of "net" gear group lengths measured in centimeters of Stoplight Parrotfish in St. Croix across time collected. Trend line is mapped across data, each point is color and shape specific to the gear it represents. The top pot uses the LAND_STANDARD_GEAR_NAME variable, as did all previous plots. The second plot uses the LAND_GEAR_NAME variable, i.e. the gear name specific to the island. This variable shows the different mesh sizes used in the net gear grouping. No significant p values for time period or gears, further comparisons not needed.
#| fig-width: 12
#| fig-height: 12

abc5
abc6

```

```{r net glm tbl}
#| echo: false
#| warning: false
#| label: tbl-tbl5_tbl-tbl6
#| tbl-cap: |
#|   This shows the results of glm analysis of the "net" gear group of Stoplight Parrotfish lengths in St. Croix. The column titled "group" indicates the group(s) that the gear can statistically be included in, and thus be statistically similar to the other gears grouped similarly. The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column inticates the percent of the total(n) recorded fish lengths that are included within each gear. The top pot uses the LAND_STANDARD_GEAR_NAME variable, as did all previous plots. The second plot uses the LAND_GEAR_NAME variable, i.e. the gear name specific to the island. This variable shows the different mesh sizes used in the net gear grouping.

tbl5
tbl6

```

\newpage

## Aggregated Gear Density

```{r all lengths agd}
#| echo: false
#| label: fig-abc7
#| fig-cap: |
#|   Aggregated density plots of lengths measured in centimeters of Stoplight Parrotfish in St. Croix grouped by assigned gear groupings. 
#| fig-width: 12
#| fig-height: 12

abc7

```

```{r diving agd}
#| echo: false
#| label: fig-abc8
#| fig-cap: |
#|   Aggregated density plot of lengths measured in centimeters of each gear within the "diving" gear group of Stoplight Parrotfish in St. Croix.
#| fig-width: 12
#| fig-height: 12

abc8

```

```{r trap agd}
#| echo: false
#| label: fig-abc9
#| fig-cap: |
#|   Aggregated density plot of lengths measured in centimeters of each gear within the "trap" gear group of Stoplight Parrotfish in St. Croix.
#| fig-width: 12
#| fig-height: 12

abc9

```

```{r net agd}
#| echo: false
#| label: fig-abc10_fig-abc11
#| fig-cap: |
#|   Aggregated density plot of lengths measured in centimeters of each gear within the "net" gear group of Stoplight Parrotfish in St. Croix. The top pot uses the LAND_STANDARD_GEAR_NAME variable, as did all previous plots. The second plot uses the LAND_GEAR_NAME variable, i.e. the gear name specific to the island. This variable shows the different mesh sizes used in the net gear grouping.  
#| fig-width: 12
#| fig-height: 12

abc10
abc11

```

```{r other agd}
#| echo: false
#| label: fig-abc12
#| fig-cap: |
#|   Aggregated density plot of lengths measured in centimeters of each gear within the "other" gear group of Stoplight Parrotfish in St. Croix.
#| fig-width: 12
#| fig-height: 12

abc12

```

\newpage

Example of how to cite sedar papers Donaldson, D.M. 2004. Overview of the State Trip Tickets Programs in the Gulf of Mexico. SEDAR7-DW-20. SEDAR, North Charleston, SC. 11pp. Poffenberger, J. 2003. Description of the Southeast Fisheries Science Center's Logbook Program for Coastal Fisheries. SEDAR-DW-29. SEDAR, North Charleston, SC. 9pp. Poffenberger, J. 2004. Commercial landings Statistics -- Red Snapper in the Gulf of Mexico. SEDAR7-DW-23. SEDAR, North Charleston, SC. 13pp. Porch, C.E., S.C. Turner, M.J. Schirripa. 2004. The Comme
