---
title: "SEDAR 84 Trip Interview Program (TIP) Size Composition Analysis of Yellowtail Snapper (Ocyurus chrysurus) in St. Thomas/St. John, US Caribbean, 1983-2022"
format: docx
editor: visual
output-file: test.docx
execute:
  cache: true
---

#### Katherine Godwin^1^, Adyan Rios^2^, Kyle Dettloff^2^

#### January 9, 2024

###### ^1^*Cooperative Institute for Marine & Atmospheric Studies, Rosenstiel School of Marine, Atmospheric, and Earth Science, University of Miami, 4600 Rickenbacker Causeway, Miami, FL 33149*

###### ^2^*National Marine Fisheries Service, Southeast Fisheries Science Center Sustainable Fisheries Division, 75 Virginia Beach Drive, Miami, FL 33149*

\newpage

## Summary

```{r}
#| echo: false
#| warning: false
#| message: false

library(here)
source(here::here('tools','sedar_84_stx_stp_2022','stx_stp_2022_figures.R'))


```

In early (what month?) 2023, the Caribbean Fishery Management Council (CFMC) requested the assistance of the National Marine Fisheries Service (NOAA Fisheries), Southeast Fisheries Science Center (SEFSC) to conduct Yellowtail Snapper assessment updates outside the SouthEast Data, Assessment, and Review (SEDAR) process. The request was to provide size composition analysis of the Trip Interview Program (TIP) data available for the St. Thomas/St. John region utilizing methods established previously in SEDAR 80 (is this the origination??). This document provides size composition analysis for Yellowtail Snaper in St. Thomas/St. John using TIP data for the years 1988 to 2022. This work was conducted by the Southeast Fisheries Science Center, Sustainable Fisheries Division, Caribbean Fisheries Branch.

There are two main portions of this document. First, gear groupings were established based on a general linear model (GLM) analysis. The GLM analysis used a gamma-distributed dependent variable. Second, the size composition of each gear grouping was assessed.

\newpage

## Generalized Linear Model (GLM) Analysis

The GLM analysis was first conducted on the time series as a whole (1988-2022), then on a truncated time series to best reflect the available commercial landings data (2012-2022), and finally on the individual gear groupings. The analysis of the full and truncated time series display the statistical similarity of all available gears to one another, regardless of gear groupings, in respect to the size of fish caught throughout. The individual gear groupings were created and analyzed based on their similar uses in the field. The gears within these groupings were compared to one another within their same group to determine if the gears perceived to be similar were statistically similar in regard to the size of fish caught throughout time. The variable LAND_STANDARD_GEAR_NAME was used as the gear indicator for analysis.

```{r all lengths GLM}
#| echo: false
#| label: fig-abc1
#| fig-cap: |
#|   Plot of all lengths measured in centimeters of Yellowtail Snapper in St. Thomas/St. John across time collected. Trend line is mapped across data, each point is color and shape specific to the gear it represents. 
#| fig-width: 11
#| fig-height: 6

abc1

```

\newpage

```{r all lengths GLM tbl}
#| echo: false
#| warning: false
#| label: tbl-tbl1
#| tbl-cap: |
#|   This shows the results of GLM analysis on the full TIP data set of Yellowtail Snapper lengths in St. Thomas/St. John. The column titled "group" indicates the group(s) that the gear can statistically be included in, and thus be statistically similar to the other gears grouped similarly. The "n" column indicates the number of unique lengths recorded for each gear. The "ID" column indicates the number of distinct trip ID's associated with each gear. The "Percentage" column inticates the percent(n_fish) of the total recorded fish lengths that are included within each gear. 
library(knitr)
kable("")
tbl1


```

add summary of statistically significant gears?

\newpage

```{r all lengths GLM 2012}
#| echo: false
#| label: fig-abc2
#| fig-cap: |
#|   Plot of all lengths measured in centimeters of Yellowtail Snapper in St. Thomas/St. John from 2012 to 2022. Trend line is mapped across data, each point is color and shape specific to the gear it represents. 
#| fig-width: 11
#| fig-height: 6

abc2

```

```{r all lengths GLM tbl 2012}
#| echo: false
#| warning: false
#| label: tbl-tbl2
#| tbl-cap: |
#|   This shows the results of GLM analysis on the TIP data set of Yellowtail Snapper lengths in St. Thomas/St. John from 2012 to 2022. The column titled "group" indicates the group(s) that the gear can statistically be included in, and thus be statistically similar to the other gears grouped similarly. The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column inticates the percent of the total recorded fish lengths that are included within each gear. 
kable("")
tbl2

```

\newpage

```{r diving GLM}
#| echo: false
#| label: fig-abc3
#| fig-cap: |
#|   Plot of "hook and line" gear group lengths measured in centimeters of Yellowtail Snapper in St. Thomas/St. John across time collected. Trend line is mapped across data, each point is color and shape specific to the gear it represents. No significant p values for time period or gears, further comparisons not needed.
#| fig-width: 11
#| fig-height: 6

abc3

```

```{r diving GLM tbl}
#| echo: false
#| warning: false
#| label: tbl-tbl3
#| tbl-cap: |
#|   This shows the results of GLM analysis of the "hook and line" gear group of Yellowtail Snapper lengths in St. Thomas/St. John. The column titled "group" indicates the group(s) that the gear can statistically be included in, and thus be statistically similar to the other gears grouped similarly. The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column inticates the percent of the total recorded fish lengths that are included within each gear. 
kable("")
tbl3

```

\newpage

```{r trap GLM}
#| echo: false
#| label: fig-abc4
#| fig-cap: |
#|   Plot of "net" gear group lengths measured in centimeters of Yellowtail Snapper in St. Thomas/St. John across time collected. Trend line is mapped across data, each point is color and shape specific to the gear it represents. 
#| fig-width: 11
#| fig-height: 6

abc4

```

```{r trap GLM tbl}
#| echo: false
#| warning: false
#| label: tbl-tbl4
#| tbl-cap: |
#|   This shows the results of GLM analysis of the "net" gear group of Yellowtail Snapper lengths in St. Thomas/St. John. The column titled "group" indicates the group(s) that the gear can statistically be included in, and thus be statistically similar to the other gears grouped similarly. The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column inticates the percent of the total recorded fish lengths that are included within each gear. 
kable("")
tbl4

```

add summary of differences between trap gears?
\newpage

```{r netst GLM}
#| echo: false
#| label: fig-abc5
#| fig-cap: |
#|   Plot of "trap" gear group lengths measured in centimeters of Yellowtail Snapper in St. Thomas/St. John across time collected. Trend line is mapped across data, each point is color and shape specific to the gear it represents.  
#| fig-width: 11
#| fig-height: 6

abc5

```

```{r netst GLM tbl}
#| echo: false
#| warning: false
#| label: tbl-tbl5
#| tbl-cap: |
#|   This shows the results of GLM analysis of the "trap" gear group of Yellowtail Snapper lengths in St. Thomas/St. John. The column titled "group" indicates the group(s) that the gear can statistically be included in, and thus be statistically similar to the other gears grouped similarly. The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column inticates the percent of the total recorded fish lengths that are included within each gear. 
kable("")
tbl5

```


\newpage

## Aggregated Gear Density

The aggregated gear density was plotted for all time periods and gear groupings for which GLM analysis was conducted. Each plot includes mean lines for each gear or gear grouping where applicable. N equals the number of individual lengths recorded for each gear or gear grouping respectively.

```{r all lengths agd}
#| echo: false
#| label: fig-abc6
#| fig-cap: |
#|   Aggregated density plots of lengths measured in centimeters of Yellowtail Snapper in St. Thomas/St. John grouped by assigned gear groupings. 
#| fig-width: 11
#| fig-height: 6

abc6

```

```{r diving agd}
#| echo: false
#| label: fig-abc8
#| fig-cap: |
#|   Aggregated density plot of lengths measured in centimeters of each gear within the "hook and line" gear group of Yellowtail Snapper in St. Thomas/St. John.
#| fig-width: 11
#| fig-height: 6

abc8

```

```{r trap agd}
#| echo: false
#| label: fig-abc9
#| fig-cap: |
#|   Aggregated density plot of lengths measured in centimeters of each gear within the "net" gear group of Yellowtail Snapper in St. Thomas/St. John.
#| fig-width: 11
#| fig-height: 6

abc9

```

```{r netst agd}
#| echo: false
#| label: fig-abc11
#| fig-cap: |
#|   Aggregated density plot of lengths measured in centimeters of each gear within the "trap" gear group of Yellowtail Snapper in St. Thomas/St. John. 
#| fig-width: 11
#| fig-height: 6

abc11

```

```{r other agd}
#| echo: false
#| label: fig-abc12
#| fig-cap: |
#|   Aggregated density plot of lengths measured in centimeters of each gear within the "other" gear group of Yellowtail Snapper in St. Thomas/St. John.
#| fig-width: 11
#| fig-height: 6

abc12

```

\newpage

Example of how to cite sedar papers Donaldson, D.M. 2004. Overview of the State Trip Tickets Programs in the Gulf of Mexico. SEDAR7-DW-20. SEDAR, North Charleston, SC. 11pp. Poffenberger, J. 2003. Description of the Southeast Fisheries Science Center's Logbook Program for Coastal Fisheries. SEDAR-DW-29. SEDAR, North Charleston, SC. 9pp. Poffenberger, J. 2004. Commercial landings Statistics -- Red Snapper in the Gulf of Mexico. SEDAR7-DW-23. SEDAR, North Charleston, SC. 13pp. Porch, C.E., S.C. Turner, M.J. Schirripa. 2004. The Comme
