---
title: "SEDAR 84 Trip Interview Program (TIP) Size Composition Analysis of Yellowtail Snapper (Ocyurus chrysurus) in St. Thomas/St. John, U.S. Caribbean, 1983-2022"
format: docx
editor: visual
output-file: sedar_84_sttj_yt_2022.docx
bibliography: references.bib
nocite: '@*'
execute:
  cache: true
---

#### Katherine Godwin^1^, Adyan Rios^2^, Kyle Dettloff^3^

#### February 8, 2024

###### ^1^*Cooperative Institute for Marine & Atmospheric Studies, Rosenstiel School of Marine, Atmospheric, and Earth Science, University of Miami, 4600 Rickenbacker Causeway, Miami, FL 33149*

###### ^2^*National Marine Fisheries Service, Southeast Fisheries Science Center Sustainable Fisheries Division, 75 Virginia Beach Drive, Miami, FL 33149*

###### ^3^*National Marine Fisheries Service, Southeast Fisheries Science Center Fisheries Statistics Division, 75 Virginia Beach Drive, Miami, FL 33149*

\newpage

## Summary

```{r}
#| echo: false
#| warning: false
#| message: false

librarian::shelf(here, knitr)
# library(here)
load(here::here('tools','sedar_84_sttj_yt_2022','sttj_yt_2022_figures.RData'))
load(here::here('tools','sedar_84_sttj_yt_2022','sttj_yt_2022_landings.RData'))


```

In preparation for SouthEast Data, Assessment, and Review (SEDAR) 84 Benchmark assessment of Caribbean Yellowtail Snapper in St. Thomas/St. John, U.S. Virgin Islands; the Southeast Fisheries Science Center, Sustainable Fisheries Division (SEFSC), Caribbean Fisheries Branch conducted a size composition analysis of the Trip Interview Program (TIP) data. This document summarizes data collected from 1983 to 2022.

The TIP data pertaining to Yellowtail Snapper in St. Thomas/St. John are comprised of `r n_all_len` length observations across `r total_trip_id_unique` unique port sampling interviews, of which `r n_fork_len` are fork lengths (`r p_fork_len`%). Two analyses are described in this document. First, gear groupings were established among gears based upon Yellowtail Snapper size composition differences among gears. Gear groups were identified based on a generalized linear mixed model (GLMM) analysis using a gamma-distributed dependent variable and a covariate to account for changes in mean size over time. Random effects for interview ID and categorical year were included to account for non-independence of observations. Second, the aggregate density of the lengths was determined based on time series and gear representation within the data.The GLM analysis of the full time series reported a statistical difference in the size of measured fish between the "LINES HAND", "POTS AND TRAPS; FISH", AND "ROD AND REEL" gears.

To understand the frequency with which trips are sampled, the number of interviews associated with main gears in the TIP data was compared to the number of trips reported in the Caribbean Commercial Landings logbook system. The `r trips_2012` TIP interviews between `r break_year` and `r max_year` make up `r tip_percentage`% of reported logbook trips. The HANDLINE and FISH_TRAP_SEINE_NET gear groupings represented the main gears reported (LINES HAND and POTS AND TRAPS; FISH). There were `r top_trips` main gear interviews (`r top_percentage`% of main gear logbook trips).

\newpage

## Data Description

The Trip Interview Program (TIP) collects length and weight data from fish landed by commercial fishing vessels. Data collection began in 1983 with frequent updates in best practices; the latest being in 2017. Data are collected by trained shore-based samplers. The trained samplers interview fishermen to obtain morphometric data and biological samples from their catch. The TIP has five primary data tables: Interview, Effort, Landing, Sample, and Observation [@beggerly2022]. The Interview, Landing, and Sample tables were utilized in this document to analyze the year, region, species, interview ID, gear name, and length values. The data were filtered to Yellowtail Snapper fork lengths in St. Thomas/St. John recorded from 1983 to 2022.

## Generalized Linear Mixed Model (GLM) Analysis

The GLM analysis of landed Yellowtail Snapper size composition among commercial fishing gears was first conducted on the time series as a whole from 1983-2022, and then on a truncated time series that best reflects the available species-specific commercial landings data from 2012-2022 (@fig-abc1). The analyses of the full and truncated time series display the statistical similarity of all available gears with respect to the mean size of fish caught throughout the time series. Gears with fewer than three interviews were excluded from the analysis.

The GLM analyses of the full time series (@tbl-tbl1) and truncated time series(@tbl-tbl2) reported a statistical difference between the "LINES HAND", "POTS AND TRAPS; FISH", AND "ROD AND REEL" gears.

\newpage

```{r all lengths GLM}
#| echo: false
#| label: fig-abc1
#| fig-cap: |
#|   Plot Plot showing relative number of Yellowtail Snapper in St. Thomas/St. John over time. Each point is color specific to the gear it represents. Gears are arranged from most to least abundant. Gray vertical line denotes the beginning of the truncated time series in 2012. 
#| fig-width: 12
#| fig-height: 8

abc1

```

\newpage

```{r all lengths GLM tbl}
#| echo: false
#| warning: false
#| label: tbl-tbl1
#| tbl-cap: |
#|   GLMM analysis summary results for St. Thomas/St. John TIP Yellowtail Snapper fork lengths(cm) from 1983 to 2022. The column titled "group" indicates the group(s) where mean lengths are not statistically different from other gears with matching group number(s). The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column indicates the percent of the total recorded lengths for each gear. Gears that make up less than 2% are shaded in gray. 
library(knitr)
kable("")

```

```{r}
#| echo: false
#| tbl-colwidths: false
#| warning: false
library(flextable)
tbl1

```

\newpage

<!-- ```{r all lengths GLM 2012} -->

<!-- #| echo: false -->

<!-- #| warning: false -->

<!-- #| label: fig-abc2 -->

<!-- #| fig-cap: | -->

<!-- #|   Plot showing relative number of Yellowtail Snapper in St. Thomas/St. John from 2012 to 2022. Each point is color specific to the gear it represents. -->

<!-- #| fig-width: 12 -->

<!-- #| fig-height: 7 -->

<!-- abc2 -->

<!-- ``` -->

```{r all lengths GLM tbl 2012}
#| echo: false
#| warning: false
#| label: tbl-tbl2
#| tbl-cap: |
#|   GLMM analysis summary results for the TIP data of Yellowtail Snapper fork lengths in St. Thomas/St. John from 2012 to 2022. The column titled "group" indicates the group(s) where mean lengths are not statistically different from other gears with matching group number(s). The "n" column indicates the number of unique lengths recorded for each gear. The "Percentage" column indicates the percent of the total recorded lengths for each gear. Gears that make up less than 2% are shaded in gray. 
library(knitr)
kable("")

```

```{r}
#| echo: false
#| tbl-colwidths: false
#| warning: false
library(flextable)
tbl2

```

\newpage

## Aggregated Gear Density

The aggregated densities of Yellowtail Snapper lengths(cm) in St. Thomas/St. John are plotted across the full and truncated time periods and by gear, respectively (@fig-abc14 and @fig-abc15). Each plot includes a vertical line associated with the respective mean length. N equals the number of individuals displayed by category.

```{r all lengths agd}
#| echo: false
#| label: fig-abc14
#| fig-cap: |
#|   Aggregated density plot of lengths(cm) of Yellowtail Snapper in St. Thomas/St. John, all gears combined. Dotted line represents mean length. 
#| fig-width: 12
#| fig-height: 8

abc14

```

<!-- \newpage -->

<!-- ```{r all lengths agd} -->

<!-- #| echo: false -->

<!-- #| label: fig-abc16 -->

<!-- #| fig-cap: | -->

<!-- #|   Aggregated density plot of lengths measured in centimeters of Yellowtail Snapper in St. Thomas/St. John from 2012 to 2022. Dotted line represents mean length.  -->

<!-- #| fig-width: 12 -->

<!-- #| fig-height: 8 -->

<!-- abc16 -->

<!-- ``` -->

\newpage

```{r diving agd}
#| echo: false
#| label: fig-abc15
#| fig-cap: |
#|   Aggregated density plot of lengths(cm) of gears with greater than 2% representation for Yellowtail Snapper in St. Thomas/St. John from 1983 to 2022. Dotted line represents mean length.
#| fig-width: 12
#| fig-height: 8

abc15

```

```{r diving agd 2012}
#| echo: false
#| label: fig-abc19
#| fig-cap: |
#|   Aggregated density plot of lengths(cm)  of gears with greater than 2% representation for Stoplight Parrotfish in St. Croix from 2012 to 2022. Dotted line represents mean length.
#| fig-width: 12
#| fig-height: 8

abc19

```

\newpage

## Literature Cited
